Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-14 paper_comparison/appendix.Rmd
refine demographic

The algorithm starts from picking a random subject $s \in S$ with the minimum number of allocated lineups. It then tries to find a lineup $l \in L$ that can maximise the distance metric $D$ and allocate it to subject $s$. Set $L$ and $s$ will be updated and the picking process will be repeated until there is no available lineups or subjects.

@@

The distance is measuring how different a lineup is from the set of lineups allocated to the subject in terms of factor values. Thus, the algorithm will try to allocate the most different lineup to a subject.

@@

The education background of most participants have Diploma or Bachelor degrees, followed by High school or below. The survey data is gender balanced. Most of the participants are between 18 to 39.

```{r education, fig.cap = "\\label{fig:education}Education distribution of subjects recuritted in this study group by age and pronoun."}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~fct_relevel(education, "High School or below", "Diploma and Bachelor Degree", "Honours Degree", "Masters Degree")) +
  xlab("Age group") +
  ylab("Count")
```

Number of participants who have previous experience in experiment about reading data plots are not very different from the number of participants who haven’t. Age distributions are also similar for these two groups.

```{r experience, fig.cap = "\\label{fig:experience}Status of pervious experience of subjects recuritted in this study group by age and pronoun."}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~previous_experience) +
  xlab("Age group") +
  ylab("Count")
```

>>>>

The algorithm starts from picking a random subject $s \in S$ with the minimum number of allocated lineups. It then tries to find a lineup $l \in L$ that can maximise the distance metric $D$ and allocate it to subject $s$. Set $L$ and $S$ will be updated and the picking process will be repeated until there is no available lineups or subjects.

@@

The distance measures how different a lineup is from the set of lineups allocated to the subject in terms of factor values. Thus, the algorithm will try to allocate the most different lineup to a subject at each step.

@@

Along with the responses to lineups, we have collected a series of demographic information including age, pronoun, education background and previous experience in studies involved data visualization. Figure \ref{fig:education} and \ref{fig:experience} provide summary of the demographic data.

As shown in Figure \ref{fig:education}, most participants have Diploma or Bachelor degrees, followed by High school or below.
The survey data is gender balanced and the majority of participants are between 18 to 39 years old.

```{r education, fig.cap = "\\label{fig:education}Education distribution of subjects recuritted in this study group by age and pronoun."}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~fct_relevel(education, "High School or below", "Diploma and Bachelor Degree", "Honours Degree", "Masters Degree")) +
  xlab("Age group") +
  ylab("Count") +
  theme_light()
```

Figure \ref{fig:experience} shows that the number of participants who have previous experience is not very different from the number of those who haven't. Age distributions are also similar for these two groups.

```{r experience, fig.cap = "\\label{fig:experience}Status of pervious experience of subjects recuritted in this study group by age and pronoun."}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~previous_experience) +
  xlab("Age group") +
  ylab("Count") +
  theme_light()
```
